---
title: "simpleRegress"
author: "Anthony Benitez"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```
```{r}
plot(WEIGHT~SEX,data=bears)
```
The bigger box is the male and the smaller one is the female so we don't have to call them bear 1 and bear 2.



## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```






## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
lmNeck = lm(LENGTH ~ NECK, data = bears)
summary(lmNeck)
```

```{r}
lmWeight = lm(LENGTH ~ WEIGHT, data = bears)
summary(lmWeight)
```

```{r}
lmChest = lm(LENGTH ~ CHEST, data = bears)
summary(lmChest)
```

```{r}
lmHeadLen = lm(LENGTH ~ HEADLEN, data = bears)
summary(lmHeadLen)
```

```{r}
lmHeadWth = lm(LENGTH ~ HEADWTH, data = bears)
summary(lmHeadWth)
```

```{r}
lmAge = lm(LENGTH ~ AGE, data = bears)
summary(lmAge)
```

1.length and head length    
2.Length and chest   
3.Length and neck  
4.length and Weight  
5.Length and Head Width  
6.Length and Age  


```{r}
mbears<-filter(bears, SEX == "1")
```

```{r}
lmNeck = lm(LENGTH ~ NECK, data = mbears)
summary(lmNeck)
```
```{r}
lmWeight = lm(LENGTH ~ WEIGHT, data = mbears)
summary(lmWeight)
```
```{r}
lmChest = lm(LENGTH ~ CHEST, data = mbears)
summary(lmChest)
```
```{r}
lmHeadLen = lm(LENGTH ~ HEADLEN, data = mbears)
summary(lmHeadLen)
```
```{r}
lmHeadWth = lm(LENGTH ~ HEADWTH, data = bears)
summary(lmHeadWth)
```
```{r}
lmAge = lm(LENGTH ~ AGE, data = mbears)
summary(lmAge)
```
















